Our Title

### 2015-05-04 draft.tex
Corrected a missing reference in the US foreign relations table.

\subsection{?????? Need better ref 11 below ????????}

\begin{table}[h]
\centering
\begin{tabular}{|c|l|}
\hline
Levels & \multicolumn{1}{c|}{Definition}                                                                                                             \\ \hline
1      & Historically and currently close relationship (Great Britain, France, Canada)                                                    \\ \hline
2      & \begin{tabular}[c]{@{}l@{}}Neither good nor bad relations or recent downturn in relations \\ For example: Germany as neutral [11] and Israel as recent downturn \cite{Goldberg2014}.\end{tabular} \\ \hline
3      & Historically and currently bad relationship (Russia, Jordan, Turkey, Egypt \cite{Office2010})                                                  \\ \hline
\end{tabular}
\caption{My caption}
\label{tab:relation_table}
\end{table}

\subsubsection{????????  This table needs a caption, reference  ???????}

>>>>

\begin{table}[h]
\centering
\begin{tabular}{|c|l|}
\hline
Levels & \multicolumn{1}{c|}{Definition}                                                                                                             \\ \hline
1      & Historically and currently close relationship (Great Britain, France, Canada)                                                    \\ \hline
2      & \begin{tabular}[c]{@{}l@{}}Neither good nor bad relations or recent downturn in relations \\ For example: Germany as neutral \cite{BBC2013} and Israel as recent downturn \cite{Goldberg2014}.\end{tabular} \\ \hline
3      & Historically and currently bad relationship (Russia, Jordan, Turkey, Egypt \cite{Office2010})                                                  \\ \hline
\end{tabular}
\caption{My caption}
\label{tab:relation_table}
\end{table}

\subsubsection{????????  This table needs a caption  ???????}

After Edward Snowden promulgated the snooping actions of the U.S. Intelligence community into its allies, Germany decided to close \enquote{friendly} intelligence cooperation \cite{BBC2013}. Consequently, it would be hard to reach an open relationship in intelligence cooperation so soon after the Snowden case. Countries in the Level 3 category were chosen because of their lack of close political relationships with the U.S., unlike the countries in Level 1 and 2.
